\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\usepackage{CormorantGaramond}
\usepackage{charter}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}

\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSingleSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.1in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

\begin{document}

\begin{center}
    {\Huge ABDULSALAM AJAY} \\ \vspace{2pt} 
    {+1 404-980-7539} ~ 
    \small{-}
    \href{mailto:dev.aj@icloud.com}{\color{blue}{dev.aj@icloud.com}} ~ 
    \small{-}
    \href{https://github.com/Sudoaj}{ \color{blue}{github.com/Sudoaj}} ~
    \vspace{-7pt}
\end{center}

\section{\color{airforceblue}EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia State University}{Atlanta, GA}
      {Bachelor of Science in Computer Science}{2018 - 2022}
    \resumeSubheading
      {Georgia State University Perimeter College}{Atlanta, GA}
      {Associate of Science in Computer Science}{2016 - 2018}
  \resumeSubHeadingListEnd
  
\section{\color{airforceblue}TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages:}{ Java, JavaScript, SQL, .NET, AngularJS, React Native} \\
     \textbf{Technologies:}{ Firebase, SQL Server, Docker, AWS} \\
     \textbf{Soft Skills:}{ Team Leadership, Problem Solving, Effective Communication, Agile Project Management} \\
     }}
 \end{itemize}
 
\section{\color{airforceblue}EXPERIENCE}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Junior .NET/ Angular Developer}{May 2022 – April 2023}
      {Cognizant Technology Solutions, Atlanta, GA}{}
      \resumeItemListStart
        \resumeItem{Engineered a dashboard website with AngularJS and .NET to enhance data visualizationand client experience.}
        \resumeItem{Leveraged SQL Server for data retrieval, boosting functionality and data precision.}
        \resumeItem{Participated in full software development lifecycle, ensuring timely delivery and quality code.}
      \resumeItemListEnd  
    \resumeSubheading
      {Media Technology Operations Associate}{July 2021 – May 2022}
      {Creative Media Industry Institute, Georgia State University, Atlanta, GA}{}
      \resumeItemListStart
        \resumeItem{Supported classrooms and labs with projectors, cameras, and various teaching equipment.}
        \resumeItem{Coordinated lab operations for Virtual Reality Demo facilities and Makerspace Augmented reality cave.}
        \resumeItem{Provided support for immersive media software technologies including Maya, Unreal, Unity, Spark AR, Xsens.}
      \resumeItemListEnd  
    \resumeSubheading
      {Technical Support Representative}{January 2017 – December 2017}
      {Computer Generated Solution, Atlanta, GA}{}
      \resumeItemListStart
        \resumeItem{Developed problem-solving strategies for diverse customer support scenarios.}
        \resumeItem{Specialized in troubleshooting and resolving a range of Windows system issues.}
      \resumeItemListEnd  
  \resumeSubHeadingListEnd

\section{\color{airforceblue}PROJECTS}    
    \resumeItemListStart
        \resumeItem{\textbf{Mentor Matching App} (React Native): A multiplatform app for matching mentors and mentees, featuring a robust Firebase backend and custom UI/UX. \href{https://github.com/Sudoaj}{\color{blue}\underline{GitHub}}}
        \resumeItem{\textbf{UT Hermes Android Application} (Java, Android): An app enabling mass message distribution across multiple platforms, developed with a focus on scalability and efficiency. \href{https://github.com/Sudoaj}{\color{blue}\underline{GitHub}}}
        \resumeItem{\textbf{Java Application for Business Record Keeping} (Java, SQL): A desktop application designed to automate and streamline business paperwork and record management. \href{https://github.com/Sudoaj}{\color{blue}\underline{GitHub}}}
    \resumeItemListEnd  

\section{\color{airforceblue}EXTRACURRICULAR ACTIVITIES}
    \resumeItemListStart
        \resumeItem{\textbf{Hack GSU}: Participated in the school-hosted hackathon, demonstrating rapid development and teamwork. Led a team of 4 students to develop a fun and interactive website in less than 3 hours. Competed with over 20+ teams.}
        \resumeItem{\textbf{Hack GSU Website}: Contributed to the development of the main event website for the Hack GSU hackathon. Collaborated with a team to implement the website using HTML/CSS and JavaScript.}
        \resumeItem{\textbf{Mk Agriculture}: Played a key role in branding and digital presence for a family-owned agricultural business. Engineered the brand identity and digital strategy, significantly contributing to the business’s market positioning and customer engagement.}
    \resumeItemListEnd  

\end{document}
